### 2022-04-05 manuscript/thesis.tex
final draft

A probabilistic forecast is a forecast to which probabilities are assigned to 
various possible outcomes. There are a number of ways whereby probabilities or 
uncertainty may be represented. A common representation is either a continuous 
or
discrete parametric distribution, given as a probability density/mass function. 
Much of the literature 
on calibration, sharpness, and scoring of a forecast pertains to parametric 
distribution forecasts
\cite[]{gneiting2007probabilistic,gneiting2013combining,baran2018combining}.
Other common representations include samples \cite[]{krueger2016probabilistic}, 
discretized bin distributions \cite[]{mcgowan2019collaborative},
and quantile forecasts \cite[]{taylor2021evaluating, bracher2021evaluating}. 
Each representation may be more or less 
appropriate than the others for a given problem but knowing how to interpret, 
score, and contruct ensemble forecasts for a selected representation is 
essential when multiple teams collaborate in the same forecasting project.

@@

Since the 2013-14 flu season, the CDC has hosted an annual competition for 
forecasting the timing, peak, and intensity of the year's flu 
season. The specific events to be forecasted are known as \emph{targets}.
Forecasts
for these different targets also include forecasts for one, two, three, and 
four weeks ahead of the prediction time. National flu data is provided weekly 
to academic teams not directly affiliated with the CDC who use that data to 
construct forecasts using 
whatever methods they choose. Historically, the forecasts must be 
submitted 
in a discretized bin distribution
format. A \emph{bin distribution} is a probability distribution represented by
breaking the numeric range of an outcome into intervals or \emph{bins} and
directly assigning the probability that the event falls within each bin.
During previous flu seasons the \emph{binning scheme} or the assignment of 
bin values was on a numeric 
scale with a bounded range and the 
prediction of a specific target was a set of probabilities assigned to each bin
\cite[]{mcgowan2019collaborative}.
These forecasts were then evaluated against actual flu activity, and at 
the end of the season a winning team was declared \cite[]{cdcflusight}.

This competition has provided the CDC, competing teams, and other interested
parties a chance to collaborate and improve their forecasting from season to
season. One 
proposed way to enhance prediction has been to aggregate the various teams'
forecasts into a \emph{multi-model ensemble forecast} 
\cite[]{mcgowan2019collaborative,mcandrew2019adaptively,reich2019accuracy},
refered to hereafter as an ensemble forecast.

@@

\section{COVID-19 Forecast Hub}
In March 2020, at the onset of the COVID-19 pandemic, the COVID-19 Forecast Hub
was founded. Borrowing from the work done in the CDC flu competition, the 
COVID-19 Forecast Hub is a central site in 
which dozens of academic teams collaborate to forecast the ongoing COVID-19 
pandemic.
Every week relevant
pandemic data is provided to these teams who construct forecasts models to 
predict the targets cases, hospitalizations, and deaths due to COVID-19. 
Forecasts are 
made on the US county,
state, and national levels and for days, weeks, and months ahead.
These forecasts are aggregated into a single ensemble forecast. The model data,
forecasts, and the ensemble forecast are passed along to the CDC for its use in 
official
communication \cite[]{Cramer2021-hub-dataset}. Figure \ref{fig:cdcoff} is an 
official CDC report from August 2021 showing forecasts from the COVID-19 
Forecast Hub of increment deaths and cumulative deaths due to COVID-19.

@@

\begin{figure}[htbp]
\centerline{\includegraphics[scale=.24]{Images/8_30_21_cvd_deaths.jpeg}}
\begin{center}
\begin{minipage}{10cm}
\captionsetup{font=scriptsize}
\caption[Official CDC COVID-19 deaths report August 2021]{This image, 
published on www.cdc.gov in August 2021 as official public communication 
by the CDC, shows forecast models for national new weekly deaths due to COVID-19 
in the top row and cumulative deaths on the bottom row. The plots in the left 
column show prediction intervals from multiple teams whereas the plots on the 
right show the intervals for an ensemble forecast model with gray lines
predicting individual model point forecasts.}
\label{fig:cdcoff}
\end{minipage}
\end{center}
\end{figure}

\section{Outline}
In the context of collaborative forecasting like that of the CDC flu competition
or the COVID-19 Forecast Hub, bin forecasts and quantile forecasts have become
important representations to those involved in the projects. Yet both 
representation types come 
with their drawbacks. Computer
storage for instance might be a concern if many bin distributions are used for 
forecasting, 
and scoring methods are limited if forecasts are quantile forecasts.

@@

In Section \ref{section:representations}, 
popular probabilistic forecast representation 
types are defined and reviewed. Methods of scoring, storing, constructing 
ensembles, and other aspects will be reviewed and compared for each 
representation type.
In Section \ref{section:conmixforc}, details for using mixture 
distributions in a collaborative forecast project are presented as well as tools
which may be used for scoring and constructing an ensemble.
Section \ref{section:retrostud} is a retrospective study of the CDC flu 
competition and COVID-19 Forecast Hub
forecasts and an attempt to assess whether forecast models
may be approximated by one component mixture distributions.

@@

\subsection{Ensemble construction}
A multi-model ensemble is a statistical model made by combining information from
two or more individual statistical models. Private and public decisions are 
regularly made after combining information from multiple sources. For any given
situation, information from one source may provide insight on a subject which 
other
sources fail to capture. Likewise one statistical model may provide insight
that another model does not so that when they are combined into an ensemble the 
ensemble outperforms the individual component models.

As probabilistic forecasting becomes more commonplace, so too does ensemble 
modeling. Ensembles have been used extensively in weather and
climate modeling \cite[]{baran2018combining}, 
and they have been used increasingly in modeling infectious disease outbreaks
\cite[]{yamana2016superensemble}. 
Ensembles allow for an incorporation of multiple signals -
often from differing data sources- and sometimes individual model biases are 
canceled
out or reduced by biases from other models \cite[see references
therein]{reich2019accuracy}. 
In several disease outbreak studies, ensemble forecasts have been 
shown to outperform individual model forecasts
\cite[see
references therein]{ray2020ensemble, cramer2021evaluation}.

@@

Other functions classified by a parameteric distribution include the cumulative
distribution function (CDF) and the inverse CDF or quantile function. The CDF 
in the continuous case is defined in \eqref{eq:ccdf} and is defined in the 
discrete case in \eqref{eq:dcdf}. Here $x_n$ is the largest value of X less than 
or equal to $x$.
The quantile function is defined in \eqref{eq:quant} which returns a quantile 
value where $p$ is a given probability such that $0\leq p \leq 1$.

@@

For a forecast represented as a parametric function with pmf/pdf $p_m(\cdot)$, 
the accuracy of the forecast may be measured by how likely realized value $x^*$
is to occur. Commonly used proper scoring rules for parametric distributions
include the logarithmic score (LogS), the
continuous rank probability score (CRPS) \cite[]{hersbach2000decomposition}
\cite[]{alves2013ncep}, and the interval/Brier 
score (IS) \cite[]{gneiting2007strictly} among 
others. See also \cite[]{gneiting2014probabilistic}
Section 3 for more on proper scoring functions. The definitions 
\eqref{eq:logs} and \eqref{eq:crps} are found in the review by Krueger.

@@

Generally computation and evaluation of parametric distribution functions is not 
hard. 
For most commonly used parametric distributions -normal, lognormal, Poisson,
gamma, etc.- there is software readily available to compute density, 
distribution, and quantile values. 
A completely defined continuous parametric distribution may be evaluated at a
continuously
infinite number of values. We will call this an infinite resolution.
And requirements for storage are low 
compared to other representation types that will be discussed. The most common
parametric distributions can be fully defined with three or pieces of data
including
the distribution family and two parameters. Table \ref{table:pstor} 
contains
enough information to completely define a $\mbox{Lognormal(1,0.4)}$ 
distribution.

\begin{table}[h!]
\begin{center}
\begin{minipage}{10cm}
\captionsetup{font=scriptsize}
\centering
 \begin{tabular}{|c c c|} 
 \hline
 family & param1 & param2 \\ [0.5ex] 
 \hline
 lnorm & 1 & 0.4 \\ 
 \hline
 \end{tabular}
 \caption[Parametric distribution storage]{This is an example of data required
 for a lognormal 
 distribution with 
 parameters $\mu = $ 1 and $\sigma =$ 0.4}
 \label{table:pstor}
 \end{minipage}
 \end{center}
\end{table}

@@

\subsection{Sample distributions}
Forecast model builders may want more flexibility in modeling than a 
parametric 
distribution can provide. Methods that require sampling from a posterior 
distribution or Bootstrap sampling to obtain a sample distribution are examples
where parametric distributions may not be appropriate for modeling because of 
the lack of flexibility in distribution shape.

@@

According to the Strong Law of Large numbers, the sample mean will converge to
the expected value of the distribution as $n \rightarrow \infty$ as long as the 
expected value of that distribution exists. Likewise by the same law the 
ECDF will converge to the true CDF 
as $n \rightarrow \infty$. Thus, if a sufficiently large 
sample is generated from a distribution with for which an expectation exists, 
the sample will closely approximate the 
true distribution.

For common distribution families it is easy to generate large samples using 
existing functions in \texttt{R} and other programming platforms. For some 
distributions 
for which the mathematical formula is unkown or is not in closed form, more 
sophisticated methods may be required to generate samples. Bayesian analyses may 
require a Gibbs sampling or a Metropolis-Hastings algorithm, among others, 
to generate a 
sample. Such samples are useful in that the true distribution may be closely 
approximated without knowing the true mathematical form.

@@

To build an ensemble model from sample distribution forecasts, the MA 
construction from (\ref{eq:bma}) may be used only replacing $p_m$ with the
approximate KD or GA pdf functions
-$\hat{p}_{n_m}^{KD}$ or $\hat{p}_{n_m}^{GA}$  
Here as well the optimal weights 
$w_m$ may be estimated by maximizing the likelihood or minimizing CRPS. 
If the desire is that the ensemble still be
a sample distribution, after selecting weights, a sample may be selected by 
randomly selecting a sample from $(X_n)_m$ with probability $w_m$.

A potentially large issue with using sample distributions is the amount of storage
it would require. For example when making MCMC draws from a posterior 
distribution, the final sample distribution can have a sample size of thousands
or tens of thousands. Maybe not all distributions would require such a large 
sample size, but sizes of at least dozens or hundreds would be required for each
forecast prediction. For any project the size of the CDC flu competition or the
COVID-19 Forecast Hub, the storage required would be large and potentially 
expensive.

@@

A bin distribution may be constructed over a set 
$A = [a, b)$ by partitioning $A$ into a set of $K$ bins $\{B_i\}_{i=1}^{K}$
where $B_i = [b_{i-1}, b_i)$ and $\cup_{i=1}^{K} B_i = A$. Based on the problem
to be forecasted, researchers will determine the possible range $A$ and 
select the number of bins and the sizes for each bin. It may be the case
that a collaborative project will set the width of all bins to be equal so that 
$\Delta = b_i - b_{i-1}$ is the same width for all $i$ 
\cite[]{mcgowan2019collaborative}.
To complete the construction, a probability $p_i$ is assigned to each $B_i$ 
where $\sum_{i=1}^{K}p_i = 1$. These probabilities are determined by the 
forecasters. 
This representation with a given bin and assigned probability may be 
treated like a discrete distribution with a pmf in that the calculations of 
moments and of the 
the cumulative distribution are done the same as for a discrete parametric 
distribution. For a random variable $X$ from a binned distribution 
the $j^{th}$ moment may be calculated as in \eqref{eq:bev}. 
Here $\beta_i$ is a value corresponding to bin $B_i$ (such as $\beta_i = b_i$,
$\beta_i = b_{i-1}$ or $\beta_i$ is the mean or mid value in $B_i$). The 
cumulative distribution may be calculated as in \eqref{eq:bcdf}.
Here $p_n$ is the probability for the bin $B_n$ where $b \in B_n$.

@@

If the value to be forecasted takes on discrete values a common discrete 
distribution, such as a binary or Poisson distribution, may sometimes be used to 
assign probabilities to each of the bins. When the values to be forecasted are
continuous, a forecaster may need to employ a method of discretization to a 
forecast distribution. There are a number of possible ways to do this including
those outlined by Chakraborty and Subrata \cite[]{chakraborty2015generating}.

The CDC flu competition has used a bin distributions as the forecast 
representation. The CDC has also used it for other disease outbreak
forecast projects.
In that context it has become the standard representation 
\cite[]{brooks2020comparing}. Much work has been done in evaluating 
and constructing ensemble models on influenza forecasts represented by 
discretized bins 
\cite[]{mcgowan2019collaborative, mcandrew2019adaptively,reich2019collaborative}.

Because discretized bins can be seen as a pmf, methods for proper scoring 
already 
discussed -LogS and CRPS- are useable and MA is valid method for ensemble 
construction. Reich et. al used MA to combine multiple forecasts from the flu 
competition. They built and compared ensemble models with different weighting
schemes including equally weighted components $w_j = 1/J$ and estimating weights
according to the model specification. To estimate weights they used the 
expectation maximization (EM) algorithm 
\cite[see
supplementary material within for details]{reich2019accuracy}.

The exact amount of information required for a discretized bin forecast will 
vary depending on the permitted range of the forecast and the desired 
resolution. 
In the CDC flu contest, a forecast might have 131 bins between 0\% and 13.1\% 
-bins having increments of 0.1 or 0.01\%- with 
corresponding probabilities in each. This makes 262 pieces of information per
prediction. For any binning scheme of more than two bins, the information 
requirement for bin distributions will be higher than for parametric 
distributions.
Table \ref{table:dbins} illustrates what a discretized 
$\mbox{Lognormal(1,0.4)}$ distribution truncated over $[0,8]$
looks like in 41 equally spaced bins. The discretization was done
such that the probabilities $p_i$ are calculated as in \eqref{eq:disc}
where $p^{TL}$ is the pdf of a truncated $\mbox{Lognormal(1,0.4)}$. This is 
similar
to Methodology-IV from Chakraborty 
\cite[]{chakraborty2015generating,kemp2004classes}.

@@

Submitted as a forecast prediction, the distribution illustrated in table 
\ref{table:dbins} 
includes 82 pieces of data. For parts 
of the CDC influenza competition some forecasts included up to 262. This is 
far less storage than the possible thousands of draws from a sample 
distribution but is 
still much larger than the three or five data pieces required to report a 
lognormal
or truncated lognormal distribution.

@@

 \end{tabular}
  \caption[Discretized bin distribution storage]{This is a storage example of a
  discretized
  lognormal with $\mu = 1$ and $\sigma = 0.4$ truncated over $[0,8]$.}
\label{table:dbins}
\end{minipage}
\end{center}
\end{table}

Besides potentially large amount of information required per forecast,
creating the right 
binning scheme may be a challenge. Because there must be a finite number of
bins, forecast distributions often have a finite support. And where the range of 
possible outcomes to a problem is not well known, the right binning scheme may 
be
hard to produce. This may depend on the details of the event to be forecasted, 
but in the case of the COVID-19 outbreak choosing the right set of bins posed
a few problems.

\subsection{Quantile representation}
When deciding how forecasts should be represented in the COVID-19 Forecast Hub,
the time pressure of generating forecasts and the large
range for possible outcomes both contributed to the COVID-19 Forecast Hub 
decision
to forego trying to create the right binning scheme and use quantile forecasts
to forecast the COVID-19 pandemic \cite[]{bracher2021evaluating}.
The COVID-19 Forecast Hub requires predictions to be submitted as 11 or three 
nominal 
intervals -depending on the specific target and unit to forecast- and a median.
Using this interval or quantile representation leads to a number of changes in 
the scoring and ensemble building of forecasts.

A quantile forecast is constructed as in \eqref{eq:quantiles}.
Here for $N$ given quantiles $\alpha_1,..., \alpha_N$; $q_1,..., q_N$ are the 
values such that 
When the quantiles are reported as prediction intervals we have 
\eqref{eq:intervals}.

@@

What is possible for scoring forecasts
or constructing ensemble in other representations is often not possible with
quantile forecasts. The shape of a distribution is also not known and in fact,
nothing is known about the tails or the uncertainty beyond the most 
extreme reported quantile values. In the COVID-19 Forecast Hub predictions, 
nothing 
is reported about the range below the $1^{st}$ quantile or above the $99^{th}$.
Yet the quantile representation has its advantages.

@@

To score a quantile forecast, 
neither the LogS nor the CRPS may be used, 
but another proper scoring rule the IS may be used.
For an observed outcome $x^*$ and a prediction interval $(l,r)$ 
where $l$ and $r$ are the $\alpha/2$ and $(1-\alpha/2)$ quantiles that bound
the central $(1-\alpha)$ prediction interval the IS is defined in \eqref{eq:is}.
This is a sum -weighted by 
$\alpha$- of the width of the
interval and the distance between $x^*$ and the interval (if $x^*$ is not 
captured in the interval) \cite[]{gneiting2014probabilistic}. 
The IS requires only a single central 
$(1-\alpha) \times 100$ prediction interval.

\begin{equation}
\label{eq:is}
  IS_{\alpha}(l,r; x^*) = (r-l) + \frac{2}{\alpha}(l-x^*)1\{x^*<l\} 
  + \frac{2}{\alpha}(y-r)1\{x^* > r\}
\end{equation}

When an quantile forecast is made up of multiple intervals each with different
$\alpha$ levels, the weighted interval score (WIS) may be used as it was by
Bracher et.
al use the WIS to score COVID-19 quantile forecasts 
\cite[]{bracher2021evaluating}.
There are multiple versions of the WIS -some of 
which are described in Bracher et. al, but the version used by the COVID-19 
Forecast
Hub for a forecast of $K$ intervals is defined in \eqref{eq:wis}.
Here $median$ refers to the predictive median and $w_k = \alpha_k/2$ is the 
weight on the $k^{th}$
interval. With that selection of weights, it may be shown that the
WIS approximates the CRPS \cite[see S1 Text therein]{bracher2021evaluating}.

@@

 \hline
 \end{tabular}
 \begin{minipage}{10cm}
 \caption[Quantiles and values storage]{This shows six quantiles
 and values from a lognormal distribution with $\mu = 1$ and $\sigma = 0.4$}
 \label{table:qstor}
 \end{minipage}
 \end{center}
\end{table}

>>>>

A probabilistic forecast is a forecast to which probabilities are assigned to 
various possible outcomes. There are a number of ways whereby probabilities or 
uncertainty may be represented. A common representation is either a continuous 
or
discrete parametric distribution, given as a probability density/mass function. 
Much of the literature 
on calibration, sharpness, and scoring of a forecast pertains to parametric 
distribution forecasts
\cite[]{gneiting2007probabilistic,gneiting2013combining,baran2018combining}.
Other common representations include samples \cite[]{krueger2016probabilistic}, 
discretized bin distributions \cite[]{mcgowan2019collaborative},
and quantile forecasts \cite[]{taylor2021evaluating, bracher2021evaluating}. 
Each representation may be more or less 
appropriate than the others for a given problem, but knowing how to interpret, 
score, and construct ensemble forecasts for a selected representation is 
essential when multiple teams collaborate in the same forecasting project.

@@

Since the 2013-14 flu season, the CDC has hosted an annual competition for 
forecasting the timing, peak, and intensity of the year's flu 
season. The specific events to be forecast are known as \emph{targets}.
Forecasts
for these different targets also include forecasts for one, two, three, and 
four weeks ahead of the prediction time. National flu data is provided weekly 
to academic teams not directly affiliated with the CDC who use that data to 
construct forecasts using 
whatever methods they choose. Historically, the forecasts have been
submitted 
in a discretized bin distribution or a bin distribution
format. A \emph{bin distribution} is a probability distribution represented by
breaking the numeric range of an outcome into intervals or \emph{bins} and
directly assigning to each bin the probability that the event falls 
within the bin.
During previous flu seasons the \emph{binning scheme} or the assignment of 
bin values was on a numeric 
scale with a bounded range and the 
prediction of a specific target was a set of probabilities assigned to each bin
\cite[]{mcgowan2019collaborative}.
These forecasts were then evaluated against actual flu activity, and at 
the end of the season a winning team was declared \cite[]{cdcflusight}.

This competition has provided the CDC, competing teams, and other interested
parties a chance to collaborate and improve their forecasting from season to
season. One 
proposed way to enhance prediction has been to aggregate the various teams'
forecasts into a \emph{multi-model ensemble forecast} 
\cite[]{mcgowan2019collaborative,mcandrew2019adaptively,reich2019accuracy},
or an ensemble forecast.

@@

\section{COVID-19 Forecast Hub}
In March 2020, at the onset of the COVID-19 pandemic, the COVID-19 Forecast Hub
was founded. Borrowing from the work done in the CDC flu competition, the 
COVID-19 Forecast Hub is a central site in 
which dozens of academic teams collaborate to forecast the ongoing COVID-19 
pandemic.
Every week relevant
pandemic data is provided to these teams who construct forecasts models to 
predict the targets cases, hospitalizations, and deaths due to COVID-19. 
Forecasts are 
made on the US county,
state, and national levels and for days, weeks, and months ahead.
These forecasts are aggregated into a single ensemble forecast. The model data,
forecasts, and the ensemble forecast are passed along to the CDC for its use in 
official
communication \cite[]{Cramer2021-hub-dataset}. Figure \ref{fig:cdcoff} is from 
an 
official CDC report from August 2021 showing forecasts from the COVID-19 
Forecast Hub of increment deaths and cumulative deaths due to COVID-19.

@@

\begin{figure}[htbp]
\centerline{\includegraphics[scale=.24]{Images/8_30_21_cvd_deaths.jpeg}}
\begin{center}
\begin{minipage}{10cm}
\captionsetup{font=scriptsize}
\caption[Official CDC COVID-19 deaths report August 2021]{This image, 
published on www.cdc.gov in August 2021 as official public communication 
by the CDC, shows forecast models for national new weekly deaths due to COVID-19 
in the top row and cumulative deaths on the bottom row. The plots in the left 
column show prediction intervals from multiple teams whereas the plots on the 
right show the intervals for an ensemble forecast model with gray lines that are
individual model point forecast predictions.}
\label{fig:cdcoff}
\end{minipage}
\end{center}
\end{figure}

\section{Outline}
In the context of collaborative forecasting like that of the CDC flu competition
or the COVID-19 Forecast Hub, bin forecasts and quantile forecasts have become
important representations. Yet both 
representation types come 
with their drawbacks. Computer
storage for instance might be a concern if many bin distributions are used for 
forecasting, 
and scoring methods are limited if forecasts are quantile forecasts.

@@

In Section \ref{section:representations}, 
popular probabilistic forecast representation 
types are defined and reviewed. Methods of scoring, storing, constructing 
ensembles, and other aspects will be reviewed and compared for each 
representation type.
In Section \ref{section:conmixforc}, details for using mixture 
distributions in a collaborative forecast project are presented as well as tools
which may be used for scoring and constructing an ensemble forecast.
Section \ref{section:retrostud} is a retrospective study of the CDC flu 
competition and COVID-19 Forecast Hub
forecasts and an attempt to assess whether forecast models
may be approximated by one component mixture distributions.

@@

\subsection{Ensemble construction}
An ensemble model is a statistical model made by combining information from
two or more individual statistical models. Private and public decisions are 
regularly made after combining information from multiple sources. For a given
problem, information from one source may provide insight on a subject which 
other
sources fail to capture. Likewise one statistical model may provide insight
that another model does not so that when they are combined into an ensemble the 
ensemble outperforms the individual component models.

As probabilistic forecasting becomes more commonplace, so too does ensemble 
modeling. Ensembles have been used extensively in weather and
climate modeling \cite[]{baran2018combining}, 
and they have been used increasingly in modeling infectious disease outbreaks
\cite[]{yamana2016superensemble}. 
Ensembles allow for an incorporation of multiple signals -often from differing
data sources- and sometimes individual model biases are 
canceled
out or reduced by biases from other models \cite[see references
therein]{reich2019accuracy}. 
In several disease outbreak studies, ensemble forecasts have been 
shown to outperform individual model forecasts
\cite[see
references therein]{ray2020ensemble, cramer2021evaluation}.

@@

Other functions classified by a parameteric distribution include the cumulative
distribution function (CDF) and the inverse CDF or quantile function. The CDF 
in the continuous case is defined in \eqref{eq:ccdf} and in the 
discrete case is defined in \eqref{eq:dcdf}.
The quantile function is defined in \eqref{eq:quant} which returns a quantile 
value where $p$ is a given probability such that $0\leq p \leq 1$.

@@

For a forecast represented as a parametric distribution 
with pmf/pdf $p_m(\cdot)$, 
the accuracy of the forecast may be measured by how likely realized value $x^*$
is to occur. Commonly used proper scoring rules for parametric distributions
include the logarithmic score (LogS), the
continuous rank probability score (CRPS) \cite[]{hersbach2000decomposition}
\cite[]{alves2013ncep}, and the interval/Brier 
score (IS) \cite[]{gneiting2007strictly} among 
others. See also \cite[]{gneiting2014probabilistic}
Section 3 for more on proper scoring functions. The definitions 
\eqref{eq:logs}, \eqref{eq:crps}, and \eqref{eq:is} are found in the review by 
Krueger.

@@

Generally computation and evaluation of parametric distribution functions is not 
hard. 
For most commonly used parametric distributions -normal, lognormal, Poisson,
gamma, etc.- there is software readily available to compute density, 
distribution, and quantile values. 
A completely defined continuous parametric distribution may be evaluated at a
continuously
infinite number of values which we call an \emph{infinite resolution}.
Also, requirements for storage are low 
compared to other representation types that will be discussed. The most common
parametric distributions can be fully defined with three or four pieces of data
including
the distribution family and two parameters. Table \ref{table:pstor} 
contains
enough information to completely define a $\mbox{Lognormal(1,0.4)}$ 
truncated on $[0,8]$ distribution. The truncation is done here so as to make a
direct comparison with the distributions shown later in Tables 
\ref{table:dbins} and \ref{table:qstor}.

\begin{table}[h!]
\begin{center}
\begin{minipage}{10cm}
\captionsetup{font=scriptsize}
\centering
 \begin{tabular}{|c c c c c|} 
 \hline
 family & param1 & param2 & lowerlim & upperlim\\ [0.5ex] 
 \hline
 lnorm & 1 & 0.4 & 0 & 8 \\ 
 \hline
 \end{tabular}
 \caption[Parametric distribution storage]{This is an example of data required
 for a lognormal 
 distribution with 
 parameters $\mu = $ 1 and $\sigma =$ 0.4}
 \label{table:pstor}
 \end{minipage}
 \end{center}
\end{table}

@@

\subsection{Sample distributions}
Forecasters may want more flexibility in modeling than a 
parametric 
distribution can provide. Methods that require sampling from a posterior 
distribution or bootstrap sampling to obtain a sample distribution are examples
where parametric distributions may not be appropriate for modeling because of 
the lack of flexibility in distribution shape.

@@

According to the Strong Law of Large numbers, the sample mean will converge to
the expected value of the distribution as $n \rightarrow \infty$ as long as the 
expected value of that distribution exists. Likewise by the same law the 
ECDF will converge to the true CDF 
as $n \rightarrow \infty$. Thus, if a sufficiently large 
sample is generated from a distribution for which an expectation exists, 
the sample will closely approximate the 
true distribution.

For common distribution families it is easy to generate large samples using 
existing functions in \texttt{R} and other programming platforms. For some 
distributions 
for which the mathematical formula is unknown or is not in closed form, more 
sophisticated methods may be required to generate samples. Bayesian analyses may 
require a Gibbs sampling or a Metropolis-Hastings algorithm, among other
sampling methods, 
to generate a 
sample. Such samples are useful in that the true distribution may be closely 
approximated without knowing the true mathematical form.

@@

To build an ensemble model from sample distribution forecasts, the MA 
construction from (\ref{eq:bma}) may be used only replacing $p_m$ with the
approximate KD or GA pdf functions
-$\hat{p}_{n_m}^{KD}$ or $\hat{p}_{n_m}^{GA}$ respectively.  
Here as well the optimal weights 
$w_m$ may be estimated by maximizing the likelihood or minimizing CRPS. 
If the desire is that the ensemble still be
a sample distribution, after selecting weights, a sample may be selected by 
randomly selecting a sample from $(X_n)_m$ with probability $w_m$.

A potentially large issue with using sample distributions is the amount of 
storage
it may require. For example when making MCMC draws from a posterior 
distribution, the final sample distribution can have a sample size of thousands
or tens of thousands. Maybe not all distributions would require such a large 
sample size, but sizes of at least dozens or hundreds would be required for each
forecast prediction. For any project the size of the CDC flu competition or the
COVID-19 Forecast Hub, the storage required would be large and potentially 
expensive.

@@

A bin distribution may be constructed over a set 
$A = [a, b)$ by partitioning $A$ into a set of $K$ bins $\{B_i\}_{i=1}^{K}$
where $B_i = [b_{i-1}, b_i)$ and $\cup_{i=1}^{K} B_i = A$. Based on the problem
to be forecast, researchers will determine the possible range $A$ and 
select the number of bins and the sizes for each bin. It may be the case
that a collaborative project will set the widths of all bins to be equal so that 
$\Delta = b_i - b_{i-1}$ is the same width for all $i$ 
\cite[]{mcgowan2019collaborative}.
To complete the construction, a probability $p_i$ is assigned to each $B_i$ 
where $\sum p_i = 1$. These probabilities are determined by the 
forecasters. 
This representation with a given bin and assigned probability may be 
treated like a discrete distribution with a pmf in that the calculations of 
moments and of the 
the cumulative distribution are done the same as for a discrete parametric 
distribution. For a random variable $X$ from a binned distribution 
the $j^{th}$ moment may be calculated as in \eqref{eq:bev}. 
Here $\beta_i$ is a value corresponding to bin $B_i$ (such as $\beta_i = b_i$,
$\beta_i = b_{i-1}$ or $\beta_i$ is the mean or mid value in $B_i$). The 
cumulative distribution may be calculated as in \eqref{eq:bcdf}.
Here $p_n$ is the probability for the bin $B_n$ where $b \in B_n$.

@@

If the value to be forecast takes on discrete values a common discrete 
distribution, such as a binary or Poisson distribution, may sometimes be used to 
assign probabilities to each of the bins. When the values to be forecast are
continuous, a forecaster may need to employ a method of discretization to a 
forecast distribution. There are a number of possible ways to do this including
those outlined by Chakraborty and Subrata \cite[]{chakraborty2015generating}.

For several flu seasons now, the CDC flu competition has used a bin distribution 
as the forecast 
representation. The CDC has also used it for other disease outbreak
forecast projects.
In that context it has become the standard representation 
\cite[]{brooks2020comparing}. Much work has been done in evaluating 
and constructing ensemble models on influenza forecasts represented by 
discretized bins 
\cite[]{mcgowan2019collaborative, mcandrew2019adaptively,reich2019collaborative}.

Because a bin distribution can be viewed as a pmf, methods for proper scoring 
already 
discussed -LogS and CRPS- are useable and MA is valid method for ensemble 
construction. Reich et. al used MA to combine multiple forecasts from the flu 
competition. They constructed and compared ensemble models with different 
weighting
schemes including equally weighted components, $w_m = 1/M$,
and estimating weights
according to the model specification. To estimate weights they used the 
expectation maximization (EM) algorithm 
\cite[see
supplementary material within for details]{reich2019accuracy}.

The exact amount of information required for a bin forecast will 
vary depending on the permitted range of the forecast and the desired 
resolution. 
In the CDC flu contest, a forecast might have 131 bins between 0\% and 13\% 
-bins having increments of 0.1 or 0.01\%- with 
corresponding probabilities in each. This makes 262 pieces of information per
prediction. For any binning scheme of more than two bins, the information 
requirement for a bin distribution will be higher than for a parametric 
distribution.
Table \ref{table:dbins} illustrates what bin distribution which was discretized 
from a 
$\mbox{Lognormal(1,0.4)}$ distribution truncated over $[0,8]$
looks like in 41 equally spaced bins. The discretization was done
such that the probabilities $p_i$ are calculated as in \eqref{eq:disc}
where $p^{TL}$ is the pdf of a truncated $\mbox{Lognormal(1,0.4)}$. This is 
similar
to Methodology-IV from Chakraborty 
\cite[]{chakraborty2015generating,kemp2004classes}. The truncation here is done
because in practice a bin forecast will generally have a finite support.

@@

Submitted as a forecast prediction, the distribution illustrated in table 
\ref{table:dbins} 
includes 82 pieces of data. For parts 
of the CDC influenza competition some forecasts included up to 262. This is 
far less storage than the possible thousands of draws from a sample 
distribution but is 
still much larger than the three or five pieces of information required to 
report a 
lognormal
or truncated lognormal distribution.

@@

 \end{tabular}
  \caption[Bin distribution storage]{This is a storage example of a
  discretized
  lognormal with $\mu = 1$ and $\sigma = 0.4$ truncated over $[0,8]$.}
\label{table:dbins}
\end{minipage}
\end{center}
\end{table}

Besides the potentially large amount of information required per forecast,
creating the right 
binning scheme may be a challenge. Because there must be a finite number of
bins, forecast distributions often have a finite support. And where the range of 
possible outcomes to a problem is not well known, the right binning scheme may 
be
hard to produce. This may depend on the details of the event to be forecast, 
but in the case of the COVID-19 outbreak choosing the right set of bins posed
a few problems.

\subsection{Quantiles}
When deciding how forecasts should be represented in the COVID-19 Forecast Hub,
the time pressure of generating forecasts and the large
range for possible outcomes both contributed to the COVID-19 Forecast Hub 
decision
to forego trying to create the right binning scheme and use quantile forecasts
to forecast the COVID-19 pandemic \cite[]{bracher2021evaluating}.
The COVID-19 Forecast Hub requires predictions to be submitted as 11 or three 
nominal 
intervals -depending on the specific target and unit to be forecast- 
and a median.
Using this quantile representation prevents the use of certain methods for 
scoring and constructing ensemble forecasts.

A quantile forecast is constructed as in \eqref{eq:quantiles}.
Here for $N$ given quantiles $\alpha_1,..., \alpha_N$; $q_1,..., q_N$ are the 
values such that we have \eqref{eq:quantiles}. 
When the quantiles are reported as prediction intervals we have 
\eqref{eq:intervals}.

@@

What is possible for scoring forecasts
or constructing an ensemble in other forecast representations is often not 
possible when using
quantile forecasts. The shape of a distribution is also not known, and in fact
nothing is known about the tails or the uncertainty beyond the most 
extreme reported quantile values. In the COVID-19 Forecast Hub forecasts, 
nothing 
is reported about the range below the $1^{st}$ quantile or above the $99^{th}$.
Yet the quantile representation has its advantages.

@@

To score a quantile forecast, 
neither the LogS nor the CRPS may be used, 
but another proper scoring rule the IS may be used.
For an observed outcome $x^*$ and a prediction interval $(l,r)$ 
where $l$ and $r$ are the $\alpha/2$ and $(1-\alpha/2)$ quantiles that bound
the central $(1-\alpha)$ prediction interval the IS is defined as 
in \eqref{eq:is}.
This is a sum -weighted by 
$\alpha$- of the width of the
interval and the distance between $x^*$ and the interval (if $x^*$ is not 
captured in the interval) \cite[]{gneiting2014probabilistic}. 
The IS requires only a single central 
$(1-\alpha) \times 100$ prediction interval.

\begin{equation}
\label{eq:is}
  IS_{\alpha}(l,r; x^*) = (r-l) + \frac{2}{\alpha}(l-x^*)1\{x^*<l\} 
  + \frac{2}{\alpha}(x^*-r)1\{x^* > r\}
\end{equation}

When a quantile forecast is made up of multiple intervals each with different
$\alpha$ levels, the weighted interval score (WIS) may be used.
Bracher et.
al use the WIS to score COVID-19 quantile forecasts 
\cite[]{bracher2021evaluating}.
There are multiple versions of the WIS, some of 
which are described in Bracher et. al, but the version used by the COVID-19 
Forecast
Hub for a forecast of $K$ intervals is defined in \eqref{eq:wis}.
Here $median$ refers to the predictive median and $w_k = \alpha_k/2$ is the 
weight on the $k^{th}$
interval. With that selection of weights, it may be shown that the
WIS approximates the CRPS \cite[see S1 Text therein]{bracher2021evaluating}.

@@

 \hline
 \end{tabular}
 \begin{minipage}{10cm}
 \caption[Quantile storage]{This shows six quantiles
 and values from a lognormal distribution with $\mu = 1$ and $\sigma = 0.4$}
 \label{table:qstor}
 \end{minipage}
 \end{center}
\end{table}
